\large Neural and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-09-07 docs/papers/sto/so.tex
FIXUP updating draft test on so param gradients

\appendix
% supplementary information of Nat. Mach. Intell.

>>>>

\vspace{1em}
\appendix
% supplementary information of Nat. Mach. Intell.

\vspace{1em}
\section{Tests on the Gradients of NN Parameters}
As discussed in the main text, our objective loss function is defined on
multiple snapshots at given times, which are constructed through interpolation
during the observation operation.
Here we perform tests on the gradients of NN parameters to check our
implementation of the observation inside the adjoint method of the $N$-body time
integration.
The gradients given by the adjoint method are compared against those given by
the AD where we disable the custom VJP of the $N$-body function, see
\autoref{fig:nn_grads_cmp}.

\begin{figure*}
  \centering
  \includegraphics[width=0.5\linewidth]{nn_grads_cmp.pdf}
  \caption{\YZ{TODO make this figure better}.
  A comparison of adjoint gradients of all parameters in the $f$ and $g$ NNs to
  those by AD.
  This test runs a \pmwd\ simulation of $128^3$ particles, with a $128^3$ mesh
  and 15 time steps.
  The size and time steps of this test case is mainly limited by the memory cost
  of the AD method.
  The two NNs $f$ and $g$ both have two hidden layers of size $[n, n]$, where
  $n$ is the size of the input layer.
  The loss function involves 3 snapshots at $a=(0.6, 0.8, 1)$.
  }
  \label{fig:nn_grads_cmp}
\end{figure*}
